---
title: "Model"
author: "ToveHjelm"
date: "2 May 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r error=TRUE}
library(glmnet)
library(Rcpp)
library(data.table)

dat <- readRDS("DATA/dat_model.Rds")

## Only keep "Retail Food Establishment"
dat <- dat[LICENSE_DESCRIPTION == "Retail Food Establishment"]
## Remove License Description
dat[ , LICENSE_DESCRIPTION := NULL]
dat <- na.omit(dat)

## Add criticalFound variable to dat:
dat[ , criticalFound := pmin(1, criticalCount)]

## Set the key for dat
setkey(dat, Inspection_ID)

## Match time period of original results
# dat <- dat[Inspection_Date < "2013-09-01" | Inspection_Date > "2014-07-01"]

##==============================================================================
## CREATE MODEL DATA
##==============================================================================
# sort(colnames(dat))
xmat <- dat[ , list(Inspector = Inspector_Assigned,
                    pastSerious = pmin(pastSerious, 1),
                    pastCritical = pmin(pastCritical, 1),
                    timeSinceLast,
                    ageAtInspection = ifelse(ageAtInspection > 4, 1L, 0L),
                    consumption_on_premises_incidental_activity,
                    tobacco_retail_over_counter,
                    temperatureMax,
                    heat_burglary = pmin(heat_burglary, 70),
                    heat_sanitation = pmin(heat_sanitation, 70),
                    heat_garbage = pmin(heat_garbage, 50),
                    # Facility_Type,
                    criticalFound),
             keyby = Inspection_ID]

saveRDS(xmat, "/DATA/xmat.Rds", overwrite = TRUE)
```


Let's have a look at the data 

```{r eval=FALSE}
#library(tidyverse)
#xmat %>% 
    #DataExplorer::GenerateReport()

```

timeSinceLast doesn't really make sense as a continous value since we have way more many 2s, so let's just turn it into three categories instead. 

```{r}
library(tidyverse)
xmat %>% 
  mutate(timeSinceLast = ifelse(xmat$timeSinceLast >=2, 2, ifelse(xmat$timeSinceLast >=1, 1, 0)))  %>% 
    mutate(criticalFound = as.factor(xmat$criticalFound)) ->
  xmat

hist(xmat$timeSinceLast)



```

Much better!
Now let's split the data into training and test data. 

```{r}

xmat %>% 
  modelr::resample_partition(c(train=0.7,test=0.3)) -> # creates an object with test and train-data
  splits 

splits %>% 
  pluck("train") %>% # picks out the training data from "splits" to a seperate object
  as_data_frame() ->
  train_raw

splits %>% 
  pluck("test") %>% # picks out the test data from "splits" to a seperate object
  as_data_frame() ->
  test_raw

```

Time to cook stuff


```{r}
library(recipes)

basic_fe <- recipe(train_raw, criticalFound ~ .) 

#1
basic_fe %>% 
  step_rm(Inspection_ID) %>%
    step_num2factor(pastSerious, pastCritical, timeSinceLast, ageAtInspection, consumption_on_premises_incidental_activity, tobacco_retail_over_counter) %>% 
    step_YeoJohnson(all_numeric())-> 
  colscleaned_fe

#2
colscleaned_fe <- prep(colscleaned_fe, verbose = TRUE)

#3
train_prep1 <- bake(colscleaned_fe, train_raw)


```

Do we need to do something about the balance of critical vs not critical?

```{r}

sum(train_prep1$criticalFound == 1)/sum(train_prep1$criticalFound == 0) 

```

Maybe. Let's do it. let's increase it to 40%.

```{r}
colscleaned_fe %>% 
  step_upsample(all_outcomes(),ratio = 0.4) %>% 
  prep(retain=TRUE) %>% 
  juice() %>% 
  bake(colscleaned_fe, .) ->
  train_prep2

sum(train_prep2$criticalFound == 1)/sum(train_prep2$criticalFound == 0) 

```
Time to create a model

```{r}
glm_unbal <- glm(criticalFound ~ .-1, "binomial",data = train_prep1)
glm_bal <- glm(criticalFound ~ .-1, "binomial", data = train_prep2)
```

```{r}
test_raw %>% 
  bake(colscleaned_fe, .) %>% 
  modelr::add_predictions(glm_bal,var="glm_bal") -> 
  test_scored
```



Let's plot our prediction for the balanced and unbalanced

```{r}
test_scored %>% 
  ggplot(aes(x=glm_bal, group=criticalFound, fill=criticalFound)) +
  geom_density(alpha =.5) +
  geom_vline(aes(xintercept=-0.9))

```

Okay, I'll keep working from here

```{r error=TRUE}
library(yardstick)

test_scored$class <- as.factor(ifelse(test_scored$glm_bal < 0, 0, 1))

test_scored %>% 
conf_mat(criticalFound, class)

test_scored %>% 
accuracy(criticalFound,class)

```

Regularization

```{r}
library(glmnetUtils)

glmnet_bal <- glmnet(criticalFound~.,
                       train_prep2,
                       family="binomial",
                       alpha=0.5, #uses a combination of l1 and l2
                       intercept = FALSE)
glmnet_bal
```
```{r}
glmnet_bal_cv <- cv.glmnet(criticalFound~.,
                             train_prep2,
                             family = "binomial",
                             alpha = 0.5)
```

```{r}
test_scored$glmnet_bal_cv <- as.vector(predict(glmnet_bal_cv,
                                                 test_scored, 
                                                 na.action = na.pass))
```
```{r}
test_scored %>% 
  ggplot(aes(x=glmnet_bal_cv, group=criticalFound, fill=criticalFound)) +
  geom_density(alpha =.5) +
  geom_vline(aes(xintercept=0))
```

